---
title: "Create hymetDP Dataset from USGS Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{usgs_create}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
Publicly available hydrological and meteorological data from USGS can be discovered and accessed from the National Water Infrastructure Service (NWIS). The NWIS can be accessed using USGS's R package, dataRetrieval. hymetDP offers users convenient dataRetrieval wrapper functions to simplify the integration of USGS data with published, hymetDP-formatted data packages.

```{r}
library(hymetDP)
```
# Create a hymetDP dataset from USGS data

## Discover USGS sites

To select specific sites using `create_USGS_hymet()`, you will need to know the site's USGS Site ID (.

Use `dataRetrieval::whatNWISsites()` to discover USGS sites by State or area.

We can get a table of all USGS stream sites that measure discharge:

```{r}
sites <- dataRetrieval::whatNWISsites(stateCd="PR", siteType="ST", parameterCd="00060")
head(sites)
```

See [USGS Site Web Service](https://waterservices.usgs.gov/rest/Site-Service.html) for a complete list of argument options for `dataRetrieval::whatNWISsites()`

## Select USGS parameters

Inspect the `supported_USGS_params` to see which USGS parameters are currently supported for conversion to hymetDP.

```{r eval=FALSE}
View(supported_USGS_params)
```

## Create the hymetDP-formatted dataset from USGS data

Specify USGS sites, parameter codes, and start and end dates as arguments to `create_USGS_hymet()` to compile and format data for the given parameters at the location and the time period.

```{r}
site <- c("06879650", "50065500")
param <- c("00060")
start <- c("2021-01-01T12:30:00Z")
end <- c("2021-01-08T12:30:00Z")

usgs_hymet <- hymetDP::create_USGS_hymet(site, param, start, end)

str(usgs_hymet)
```

## Write hymetDP tables to file

```{r}
path = tempdir()

hymetDP::write_tables(
  path = path,
  DataValues = usgs_hymet$DataValues,
  Variables = usgs_hymet$Variables,
  Methods = usgs_hymet$Methods,
  Sources = usgs_hymet$Sources,
  Sites = usgs_hymet$Sites,
  QualityControlLevels = usgs_hymet$QualityControlLevels,
  SeriesCatalog = usgs_hymet$SeriesCatalog)
```

## Create EML

Create Ecological Metadata Language (EML) metadata for the derived dataset.

```{r}
# Coming soon!
```
